The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task

### 2017-07-13 docs/language_constraint_conll_camera_ready.tex
Fixed a small reference problem Table 3, as well as a link problem at the end of the introduction

\documentclass[11pt,a4paper]{article}
\usepackage{authblk}
\usepackage[hyperref]{acl2017}
\usepackage{times}
\usepackage{multirow}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage[normalem]{ulem}
\usepackage{url}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usepackage{subfig}% http://ctan.org/pkg/subfig

@@

\begin{table}[!t]
\small
\begin{center}
\begin{tabular}{|l|r|} \hline
{\bf Model} & {\bf Acc.} \\ \hline
{DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
{ukp} \cite{Mihaylov:2017} & 0.711\\ 
{tbmihaylov} \cite{Mihaylov:2017} & 0.724\\ 
$\dagger$EndingsOnly \cite{Cai:2017} & 0.725 \\
{cogcomp}  & 0.744 \\ 
{HIER,ENCPLOTEND,ATT} \cite{Cai:2017} & 0.747 \\\hline\hline
{RNN}		& 0.677 \\ 
$\dagger${Ours} & {0.724} \\ 
{\bf Combined (ours + RNN)} & {\bf 0.752} \\ \hline\hline
Human judgment & 1.000 \\ \hline
\end{tabular}
\end{center}
\caption{\label{cloze_results} Results on the test set of the  story cloze task.
The middle block are our results.
{\it cogcomp} results and human judgement scores are taken from \citet{Mostafazadeh:2017}.
Methods marked with ($\dagger$) do not use the story context in order to make a prediction.}
\end{table}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage{authblk}
\usepackage[hyperref]{acl2017}
\usepackage{times}
\usepackage{multirow}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage[normalem]{ulem}
\usepackage{url}
\usepackage{breakurl}
%\usepackage[breaklinks]{hyperref}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usepackage{subfig}% http://ctan.org/pkg/subfig

@@

\begin{table}[!t]
\small
\begin{center}
\begin{tabular}{|l|r|} \hline
{\bf Model} & {\bf Acc.} \\ \hline
{DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
{ukp} \cite{Bugert:2017} & 0.717\\ 
{tbmihaylov} \cite{Mihaylov:2017} & 0.724\\ 
$\dagger$EndingsOnly \cite{Cai:2017} & 0.725 \\
{cogcomp}  & 0.744 \\ 
{HIER,ENCPLOTEND,ATT} \cite{Cai:2017} & 0.747 \\\hline\hline
{RNN}		& 0.677 \\ 
$\dagger${Ours} & {0.724} \\ 
{\bf Combined (ours + RNN)} & {\bf 0.752} \\ \hline\hline
Human judgment & 1.000 \\ \hline
\end{tabular}
\end{center}
\caption{\label{cloze_results} Results on the test set of the  story cloze task.
The middle block are our results.
{\it cogcomp} results and human judgement scores are taken from \citet{Mostafazadeh:2017}.
Methods marked with ($\dagger$) do not use the story context in order to make a prediction.}
\end{table}
